A novel 1000\,\,MW double-reheat ultra supercritical system with turbine-extraction-heated air preheaters and low temperature economizers

### 2018-01-25 article.tex
1修改了文章的结构改为先介绍两个系统 ，再建模 2完成到用分析部分

\usepackage{amssymb,hyperref,booktabs,multirow}
% \usepackage{graphicx}%插入图片

@@

% \usepackage{amsmath}%数学公式、矩阵、积分求和等

@@

\section{Introduction}
\label{sec:1}
Coal is still the main fossil fuel resources for electricity production in the world according to~\cite{Ouedraogo2013Energy}. 
In China, coal –fired power generation accounts for more than 70\% of the total electricity generation and subsequently contribute almost 50\%, 37\%, 33\% and 55\% to the SO$_X$, NO$_X$, dust and CO$_X$ emission volumes respectively~\cite{Zhang2010Analysis}.
Statics show that China has been the largest producer and consumer of energy all over the world since 2013 [??]. 
For 2016 as a whole, Chinese coal production fell by 7.9\% and the price of steam coal increased by over 60\%[??]. 
Improve system efficiency and reducing coal consumption is still the main task of power plant design. Nowadays, ultra-supercritical (USC) power plants with large capacity and high parameter are considered to be feasible means to save energy and have rapidly developed word-wide.
The double reheat USC unit is a new generation of USC unit which can improve the thermal performance compared with single reheat units~\cite{Zhao2017Exergy}. 
According to Ref.~\cite{Yaxiu2013Thermal}, a double reheat unit with the inlet parameter 30.0\,MPa/600/620/620$^\circ$C improves the heat efficiency by 2.4\%-2.6\%, compared with a common used USC unit with the inlet parameter 25.0\,MPa/600/600$^\circ$C.
 The U.S. built the first double reheat unit with main parameter 34.4 MPa/649/566/566$^\circ$C in 1960s.
 Two 700 MW double reheat USC units in Japan were put into operation in 1990. 
 The Taizhou power plant in China began to build double reheat USC units in 2012, and put it into operation in 2015.
 Over the past few decades, the double reheat USC units have received more and more attention for its rapid development all over the world. Zhao Z et al.~\cite{Zhao2017Exergy} studied the exergy distribution system for a 1000\,MW double reheat USC power plant and provided the main reasons that led to exergy loss on the steam turbine.
 Rashidi et al.~\cite{Rashidi2014Thermodynamic} investigated the thermodynamic analysis of a double reheat steam power plant.
 According to Ref.~\cite{Wu2014Component}, component and process based exergy evaluation was performed on a coal-fired power plant in China, which provides guidance for energy-saving strategies.
 It pointed out that the exergy loss in the heat transfer process accounts for the largest proportion.

@@

\section{Reference system introduction and analysis}
\label{sec:2}
\subsection{Introduction of reference system} % (fold)
\label{sub2:intro}

% subsection subsection_name (end)

A typical coal-fired double reheat USC power plant in operation is chosen as the reference unit.
The parameter settings that maximize continuous power are 310\,bar/600$^\circ$Cfor the main steam, 610$^\circ$C for the reheat steam pressure, 33.5\% for the proportion of the single reheat steam pressure to the main steam pressure, and 33\% for the proportion of the double reheat steam pressure to the single reheat steam pressure[6].
The output power of the double reheat unit under the condition of THA load is 1000 MW.
The unit consists of one super high pressure turbine (VHP), one high pressure turbine (HP), one intermediate pressure turbine (IP), and two low pressure turbines (LP).
10-stage regenerative system with four high pressure regenerative heaters (HRH), five low pressure regenerative heaters (LRH), and one deaerator (DEA) are adopted.
Besides two additional outer steam coolers (AOC1, AOC2) are used to cool two extractions due to its high super-heating degree. The exhaust steam pressure of the steam turbine is set 4.5\,kPa. The simplified schematic of the unit is presented in Fig~\ref{fig:reference_system}.

@@

\subsection{Thermal performance evaluation of reference system} % (fold)
\label{sub2:eval}
The main  parameters of the reference system are shown in Table~\ref{tab:ref input}.

\begin{table}[htbp]
\caption{The main input parameter of reference system }
\label{tab:ref input}
\centering

\begin{tabular}{lll}
\toprule 
Items & Unit & Value\tabularnewline
\midrule
Live steam mass flow rate          	&t/h  &2533  			\\
Second reheater  		&Mass flow   	&2002\,t/h \tabularnewline
                     	& Pressure 	     &311.4\,bar 			&Second reheater inlet	&Pressure     	&3.29\,bar \tabularnewline
                     	& Temperature    &605$^\circ$C      	&  						&Temperature  	&433$^\circ$C \tabularnewline
First reheater      	&Mass flow       &2318\,t/h  			&Second reheater outlet	&Pressure     	&3.05\,bar \tabularnewline
First reheater inlet	& Pressure       &105.3\,bar 			&  						&Temperature  	&613$^\circ$C \tabularnewline
                     	&Temperature     &427$^\circ$C      	&Feedwater  			&Temperature 	&314$^\circ$C \tabularnewline
First reheater outlet	&Pressure        &103.2\,bar 			&Turbine exhaust 		&pressure 		&4.5 kPa \tabularnewline
                     	& Temperature    &6137$^\circ$C 		& 						&  				& \tabularnewline
\bottomrule
\end{tabular}	
\end{table}

Table 2 gives the temperature profiles and exergy efficiency of regenerative heaters and the air preheater, revealing the energy match level of heat exchangers.
For the air preheater, the temperature of flue gas at the inlet of the air preheater is 376$^\circ$C under THA condition, while the temperature of the air to be heated by the flue is 25$^\circ$C, leading to the exergy loss of 27.17\,MW. The temperature difference of the air preheater is calculated to be 72$^\circ$C, and average temperature of the air is 177$^\circ$C, causing the exergy efficiency of 77.16\%.
\begin{table}[htbp]
\caption{fluid parameters of heat exchangers and air preheater}
\label{tab:reheater parameter}
\centering
\small
\begin{tabular}{ccccc}
\toprule 
\multirow{2}{2cm}{Components} & \multirow{2}{2cm}{Hot fluid pressure(bar)} &\multirow{2}{2.5cm}{Hot fluid temperature($^\circ$C)} & \multirow{2}{2.5cm}{Cold fluid temperature($^\circ$C)} & \multirow{2}{3.5cm}{Fluid temperature difference($^\circ$C)}\tabularnewline
&&&&\tabularnewline
\midrule
APH &  & 376．00 & 23.00 & 353.00\tabularnewline
AOC1 &  & 526.56 & 304.51 & 222.05\tabularnewline
AOC2 &  & 527.48 & 304.51 & 222.97\tabularnewline
HRH1 &  & 417.07 & 273.62 & 143.45\tabularnewline
HRH2 &  & 314.53 & 240.73 & 73.8\tabularnewline
HRH3 &  & 434.54 & 205.89 & 228.65\tabularnewline
HRH4 &  & 316.51 & 186.48 & 130.03\tabularnewline
DEA &  & 447.37 & 163.63 & 283.74\tabularnewline
LRH6 &  & 394.01 & 140.46 & 253.55\tabularnewline
LRH7 &  & 313.17 & 104.49 & 208.68\tabularnewline
LRH8 &  & 191.84 & 82.42 & 109.42\tabularnewline
LRH9 &  & 116.61 & 59.25 & 	57.36\tabularnewline
\bottomrule
\end{tabular}
\end{table}
\normalsize

\section*{References}
\bibliographystyle{elsarticle-num}

>>>>

\usepackage{amssymb,hyperref,booktabs,multirow}
\usepackage{enumerate}

% \usepackage{graphicx}%插入图片

@@

 \usepackage{amsmath}%数学公式、矩阵、积分求和等

@@

\section{Introduction}
\label{sec1:intro}
Coal is still the main fossil fuel resources for electricity production in the world according to~\cite{Ouedraogo2013Energy}. 
In China, coal –fired power generation accounts for more than 70\% of the total electricity generation and subsequently contribute almost 50\%, 37\%, 33\% and 55\% to the SO$_X$, NO$_X$, dust and CO$_X$ emission volumes respectively~\cite{Zhang2010Analysis}.
Statics show that China has been the largest producer and consumer of energy all over the world since 2013 [??]. 
For 2016 as a whole, Chinese coal production fell by 7.9\% and the price of steam coal increased by over 60\%[??]. 
Improve system efficiency and reducing coal consumption is still the main task of power plant design. Nowadays, ultra-supercritical (USC) power plants with large capacity and high parameter are considered to be feasible means to save energy and have rapidly developed word-wide.
The double reheat USC unit is a new generation of USC unit which can improve the thermal performance compared with single reheat units~\cite{Zhao2017Exergy}. 
According to Ref.~\cite{Yaxiu2013Thermal}, a double reheat unit with the inlet parameter 30.0\,MPa/600/620/620$^\circ$C improves the heat efficiency by 2.4\%-2.6\%, compared with a common used USC unit with the inlet parameter 25.0\,MPa/600/600$^\circ$C.
 The U.S. built the first double reheat unit with main parameter 34.4 MPa/649/566/566$^\circ$C in 1960s.
 Two 700 MW double reheat USC units in Japan were put into operation in 1990. 
 The Taizhou power plant in China began to build double reheat USC units in 2012, and put it into operation in 2015.
 Over the past few decades, the double reheat USC units have received more and more attention for its rapid development all over the world. Zhao Z et al.~\cite{Zhao2017Exergy} studied the exergy distribution system for a 1000\,MW double reheat USC power plant and provided the main reasons that led to exergy loss on the steam turbine.
 Rashidi et al.~\cite{Rashidi2014Thermodynamic} investigated the thermodynamic analysis of a double reheat steam power plant.
 According to Ref.~\cite{Wu2014Component}, component and process based exergy evaluation was performed on a coal-fired power plant in China, which provides guidance for energy-saving strategies.
 It pointed out that the exergy loss in the heat transfer process accounts for the largest proportion.

@@

\section{System optimization of double reheat USC system}
\label{sec2:system intro}
\subsection{reference system on operation} % (fold)
\label{sub2:ref intro}
A typical coal-fired double reheat USC power plant in operation is chosen as the reference unit.
The parameter settings that maximize continuous power are 310\,bar/600$^\circ$Cfor the main steam, 610$^\circ$C for the reheat steam pressure, 33.5\% for the proportion of the single reheat steam pressure to the main steam pressure, and 33\% for the proportion of the double reheat steam pressure to the single reheat steam pressure[6].
The output power of the double reheat unit under the condition of THA load is 1000 MW.
The unit consists of one super high pressure turbine (VHP), one high pressure turbine (HP), one intermediate pressure turbine (IP), and two low pressure turbines (LP).
10-stage regenerative system with four high pressure regenerative heaters (HRH), five low pressure regenerative heaters (LRH), and one deaerator (DEA) are adopted.
Besides two additional outer steam coolers (AOC1, AOC2) are used to cool two extractions due to its high super-heating degree. The exhaust steam pressure of the steam turbine is set 4.5\,kPa. The simplified schematic of the unit is presented in Fig~\ref{fig:reference_system}.

@@

The main  parameters of the reference system are shown in Table~\ref{tab:ref input}.

\begin{table}[htbp]
\caption{The main input parameter of reference system }
\label{tab:ref input}
\centering
\begin{tabular}{lll}
\toprule 
Items & Unit & Value\tabularnewline
\midrule
 Live steam mass flow rate 	    	&t/h 			&2533 \\
 Live steam pressure 		    	&bar 			&310\\
 Live steam temperature		     	&$^\circ$C		&600		\\
 First reheat steam pressure    	&bar			&100.9		\\
 First reheat steam temperature  	&$^\circ$C		&610		\\
 Second reheat steam pressure    	&bar			&30.8		\\
 Second reheat steam temperature 	&$^\circ$C		&610		\\
 Power generation output 			&MW				&1000		\\
\bottomrule
\end{tabular}	
\end{table}
Table 2 gives the temperature profiles and exergy efficiency of regenerative heaters and the air preheater, revealing the energy match level of heat exchangers.
For the air preheater, the temperature of flue gas at the inlet of the air preheater is 376$^\circ$C under THA condition, while the temperature of the air to be heated by the flue is 25$^\circ$C, leading to the exergy loss of 27.17\,MW. The temperature difference of the air preheater is calculated to be 72$^\circ$C, and average temperature of the air is 177$^\circ$C, causing the exergy efficiency of 77.16\%.
\begin{table}[htbp]
\caption{fluid parameters of heat exchangers and air preheater}
\label{tab:reheater parameter}
\centering
\begin{tabular}{cccc}
\toprule 
\multirow{2}{2cm}{Components} &\multirow{2}{2.7cm}{Hot fluid temperature($^\circ$C)}  & \multirow{2}{2.7cm}{Cold fluid temperature($^\circ$C)}&  \multirow{2}{2.5cm}{LMTD($^\circ$C)}\tabularnewline
&&&\tabularnewline
\midrule
APH  &  376.00 	& 23.00  & 72.4\tabularnewline
AOC1 &   526.56 & 304.51 & 69.75\tabularnewline
AOC2 &  527.48 	& 304.51 & 60.81\tabularnewline
HRH1 &   417.07 & 273.62 & 10.64\tabularnewline
HRH2 &   314.53 & 240.73 & 10.77\tabularnewline
HRH3 &   434.54 & 205.89 & 12.68\tabularnewline
HRH4 &   316.51 & 186.48 & 6.88\tabularnewline
LRH6 &  394.01 	& 140.46 & 13.19\tabularnewline
LRH7 &   313.17 & 104.49 & 15.87\tabularnewline
LRH8 &   191.84 & 82.42  & 9.82\tabularnewline
LRH9 &   116.61 & 59.25  & 10.03\tabularnewline
\bottomrule
\end{tabular}
\end{table}

Compared with the air preheater, the regenerative heaters have lower logarithm mean temperature difference (LMTD).
However, it is found that the temperature difference between the hot and cold stream at the inlet high temperature regenerative heaters is also relatively large, which causes irreversible loss. To reduce the superheat degree of the 2nd and 4th extractions and to heat feedwater, two additional outer steam coolers are installed.
Results show that the inlet temperature difference of HRH2 and HRH4 is greatly reduced, and the exergy efficiency is improved correspondingly.
However, the inlet temperature difference between the cold and hot stream of other high temperature regenerative heaters remains very high.
Moreover, because of the material restriction of the water wall, the temperature of feedwater at the inlet of boiler is restricted to 315$^\circ$C. 
In the reference system, the first extraction has to be throttled to ensure the temperature of feedwater not exceeding the restriction.
The pressure of the first extraction is throttled from 106.70 bar to 88.56 bar, and the temperature is decreased from 425.60$^\circ$C to 413.77$^\circ$C. The throttling of the first extraction will certainly cause extra irreversible loss.
%2.2
\subsection{Proposal of a novel system with EAPH and LPE}
\label{sub2:prop novel sys}

The  layout of the optimization system is presented in Fig~\ref{fig:novel_system}.
In the optimization system, the air is not heated by flue gas in the conventional air preheater, and 8 new air preheaters (APH1\-APH8) using several extractions to heat the air is adopted.
The new air preheater is similar with regenerative heaters in function.
As shown in Fig~ the extracted steam is sent to the regenerative heater to heat the condensate or feedwater, and then the drainage from the air preheater joins with that of corresponding regenerative heater.
It should be mentioned that not all the extractions are available for air heating
For the last two stage extractions, their pressure is much lower than barometric pressure which makes it extremely difficult to maintain such low pressure environment inside the heat exchangers, and APH8 shall be shut down under low load for the same reason.
Besides, to reduce the superheat degree of extractions entering the heat exchangers and to improve the air temperature, four additional outer steam coolers (AOC1- AOC4) are installed at the outlet of APH1.
Since extractions from the 2nd to the 5th have superheat degree, they are sent to AOCs in the order of temperature level.
For example, the 2nd extraction has the highest temperature, and is applied to heat the air in the 1st AOC, and then the cooled steam from AOC1 is sent to HRH2 and air APH2 to heat the water and air respectively.

\begin{figure}[htbp]
\centering
\includegraphics[width=0.9\textwidth]{fig/novel_system}
\caption{Schematic of the novel system} 
\label{fig:novel_system}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.3\textwidth]{fig/extraction_heat_APH}
\caption{Process flow diagram of RH and APH} 
\label{fig:extraction_heat_APH}
\end{figure}
As shown in Fig~\ref{fig:novel_system}, the flue gas at the outlet of economizer is utilized to heat the condensate and feed water by four LPEs, which are paralleled to HRH2, HRH4, LRH6, and LRH8 respectively. 
Part of the condensate and feed water at the inlet of regenerative heater are sent to the LPE, then the heated water join with the main feedwater/condensate. 
Considering the acid dew point temperature, the flue gas temperature at the outlet of the last LPE is set 95℃. 
The temperature of heated water from LPE is set little higher than the feedwater from the corresponding regenerative heater.%

\section{Model establishment and thermodynamic evaluation} % (fold)
\label{sec3:modle est and eval}
\subsection{Model description and system analysis method} % (fold)
\label{ssub:model_establishment_and_system_analysis_method}

\subsubsection{Model establish method and main assumption}
\label{ssub3:modle description}
In this paper, the thermodynamic cycle of the thermal system under different loads are simulated with EBSILON® Professional for its flexibility and level of detail. 
EBSILON is a power plant simulation tool which can calculate thermodynamic quantities. 
The simulation model gives the detailed data with high degree of reliability to calculate the thermodynamic state.
EBSIOLON's simulation and parameter calculation of the equipment is based on experimental characteristics of units during the process of modeling design and off-design conditions.
However, only some characteristic curves of turbine can actually be obtained, while boiler and heat exchanger data cannot be obtained, which can only use the system built-in data as an alternative.
It’s needed to assume that the difference between the built-in data and the actual data to meet the error requirements.
The following assumptions need to be made in order to be able to simulate correctly.
\begin{enumerate}[(1)]
\item Both novel and reference systems are operated in stable condition
\item The thermal efficiency of the equipment is calculated from the thermal balance of the input and output parameters of the components, assuming that the calculation error requirement can be met.
\item According to the heat map, set the upper and lower end difference of the heat exchanger as a fixed value, and do not change among different condition.
\item  Do not take the pips' complexity and equipment’s installation difficulty of the novel system as consideration.
\end{enumerate}

\subsubsection{System analysis method} %(fold)
\label{ssub3:analsys method} 
%为了能够对优化系统与参考系统进行评估，揭示系统优化的内在机理，本文引入热力学第二定律的分析方法即用分析方法。
Exergy analysis, is adopted to reveal the location, the magnitude and the sources of thermodynamic inefficiencies of the unit.
Usually, exergy loss and exergy efficiency are chosen as evaluation indices of the thermal system or an individual component, 
The general exergy balance of component can be expressed in the following form:
\begin{equation}
\dot{I}=\sum\dot{E}{}_{in}-\sum\dot{E}{}_{out}+\sum\dot{W}{}_{in}-\sum\dot{W}{}_{out}
\end{equation}
\begin{equation}
\eta=\frac{\dot{E}{}_{earned}}{\dot{E}{}_{cost}}
\end{equation}

% subsubsection subsubsection_name (end)
\section*{References}
\bibliographystyle{elsarticle-num}
